Preliminary Thesis Defence

### 2013-11-13 draft.Rnw
minor
add packages, add bibliography
revert to book docu class
add morris shin citation

\documentclass[a4paper]{report}
\usepackage{subfiles}
\usepackage{hyperref}

@@

@@

\maketitle

\tableofcontents

\chapter*{Introduction}
jade

\chapter{South Africa}
a la duflo

\chapter{Surviving Andersonville}
article

@@

\chapter{Morris Shin 1998, Unique equilibrium in a model of self-fulfilling currency attacks}
\subfile{MorrisShin.tex}

\chapter*{End notes}

>>>>

\documentclass[a4paper]{book}
\usepackage{subfiles}
\usepackage{mathtools}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage[authordate,backend=biber]{biblatex-chicago}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}

@@

\let\oldmarginpar\marginpar
\renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\footnotesize #1]
{\raggedright\footnotesize #1}}

\addbibresource{bibliography.bib}

\newbibmacro{string+doiurlisbn}[1]{%
  \iffieldundef{doi}{%
    \iffieldundef{url}{%
      \iffieldundef{isbn}{%
        \iffieldundef{issn}{%
          #1%
        }{%
          \href{http://books.google.com/books?vid=ISSN\thefield{issn}}{#1}%
        }%
      }{%
        \href{http://books.google.com/books?vid=ISBN\thefield{isbn}}{#1}%
      }%
    }{%
      \href{\thefield{url}}{#1}%
    }%
  }{%
    \href{http://dx.doi.org/\thefield{doi}}{#1}%
  }%
}

\DeclareFieldFormat{title}{\usebibmacro{string+doiurlisbn}{\mkbibemph{#1}}}
\DeclareFieldFormat[article,incollection]{title}%
    {\usebibmacro{string+doiurlisbn}{\mkbibquote{#1}}}

@@

\frontmatter
\maketitle
\tableofcontents

\chapter{Introduction}
jade

\mainmatter
\chapter{South Africa}
a la duflo

\subfile{surviving.tex}

@@

\subfile{morrisShin.tex}

\backmatter
\chapter{End notes}

\printbibliography
